The impact of cosmic variance on simulating weak lensing surveys

### 2015-02-26 Writeup/reply.tex
list of changes added

\begin{shaded}
Is there an expectation that the 'neutral' bins should fall between OD and UD bins in all or some of the scatter plots? That doesn't seem to be the case for all. The trend when considering the neutral points confuses the conclusion of an effect due to structure in some quantities/plots. These points should be addressed explicitly. For example, presumably $f_{bulge}$ in the neutral bins should fall between OD and UD bins, given the argument at the end of page 13. It is hard to see from Fig. 15 that this is the case, and thus whether the difference between OD and UD bins is significant at all, which would not support the suggested mitigation method (b) discussed on page 13, which fig 15 is meant to test.
\end{shaded}

Not really. It is difficult to make any definitive statements about the behavior in neutral bins. As
we have verified and pointed out in Section 4.2 of the revised papern,
the neutral bins in our sample consist of mixtures of clear overdensities and underdensities, making
it look like roughly neutral in the number count. However, given the complex mixture of morphologies
plus the fact that more of the galaxies are in the overdense regions, the quantities measured are
more similar to those in overdense regions.  We have explained this in the new version, showed other
papers that verify the mixed nature of these regions, and believe this explanation should be enough
that the behavior of the neutral regions does not weaken our overall conclusions.

\rachel{Arun, if you have made other edits (fixes to bugs in figures etc.) then you should mention
  them here.  You can simply say ``In addition to the above changes, we made several small
  modifications that are not in response to the referee's comments.'' and then say what those
  changes are.  The referee deserves a chance to comment on them and it's easier for them if you
  point them out.}
\end{document}

>>>>

\begin{shaded}
Is there an expectation that the `neutral' bins should fall between OD and UD bins in all or some of the scatter plots? That doesn't seem to be the case for all. The trend when considering the neutral points confuses the conclusion of an effect due to structure in some quantities/plots. These points should be addressed explicitly. For example, presumably $f_{bulge}$ in the neutral bins should fall between OD and UD bins, given the argument at the end of page 13. It is hard to see from Fig. 15 that this is the case, and thus whether the difference between OD and UD bins is significant at all, which would not support the suggested mitigation method (b) discussed on page 13, which fig 15 is meant to test.
\end{shaded}

Not really. It is difficult to make any definitive statements about the behavior in neutral bins. As
we have verified and pointed out in Section 4.2 of the revised paper,
the neutral bins in our sample consist of mixtures of clear overdensities and underdensities, making
it look like roughly neutral in the number count. However, given the complex mixture of morphologies
plus the fact that more of the galaxies are in the overdense regions, the quantities measured are
more similar to those in overdense regions.  We have explained this in the new version, showed other
papers that verify the mixed nature of these regions, and believe this explanation should be enough
that the behavior of the neutral regions does not weaken our overall conclusions.

{\bf List of changes made}
\begin{enumerate}
\item Different linestyles are used in Figs.1-8 for the reader to be able to distinguish between the curves in black \& white, in response to referee's first comment.
\item A new paragraph has been added (in red color) towards the end of Sec. 4.2 in page 13, in response to the referee's second comment.
\item A new paragraph has been added (in red color) towards the end of page 12, in response to the referee's third comment. \\
\end{enumerate}

In addition to the above changes, we made a few minor modifications that is not in response to the referee's comments. \\

\begin{enumerate}\addtocounter{enumi}{3}
\item In Table 1, the overdense redshift bin 0.65-0.75 is now split into two bins, one from 0.65-0.7 and the other from 0.7-0.75. This is now in accordance
      with the other plots we show ( for example, Figs. 9-12)
\item We found a minor bug in the script that generated Fig.15 in the paper. We have fixed it.
\item We have thanked the referee in the `Acknowledgments' section for his/her useful comments.
\end{enumerate}

\end{document}
